Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-16 tuningpredictor.tex
typos

These results prompt for a change to standard methods in software analytics.
At least for defect prediction, 
it is no longer enough to just run a data miner and present the result
{\em without} first conducting a tuning optimization study.
The implications for other kinds of software analytics is now an open and pressing questions.

@@

\begin{raggedleft}
{\em ``So those who are last now will be first then, \\
and those who are first will be last.''}\\ 
-- Matthew 20:16

 \end{raggedleft}

@@

To the best of our knowledge, this paper is the first extensive exploration 
of applying automatic optimizers to tune data miners for defect prediction,
(though see~\cite{cora10,balogh12,Minku13,minku13z} for tuning effort estimators).
The one similar study  we can find in the period 2004 to 2014\footnote{See the GECCO and SSBSE proceedings at    goo.gl/2MY602 and goo.gl/uzvU8e.} was
Bouktiff et al.~\cite{Bouktif06} who used  simulated annealing to tune Bayes classifiers.
That was a very limited study, applied to a  single defect data set.
The analysis of this paper is far more extensive and offers the following novel result:
\bi
\item
Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
of those learners. 
\ei
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

Thirdly, it is standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
we have defended that approach on methodological grounds arguing that it
encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
can no longer be condoned. For example, one such default setting
  in the Python \mbox{SciKitLearn} toolkit~\cite{scikit-learn}
is to use $F=10$ decision trees in  Random Forest classifiers.
Our optimizer settled on  $F$ values that were nowhere near that default:

@@

In summary,it is now an open and pressing research issue to check if
analytics without parameter tuning is considered {\em harmful} or, at the 
very least, {\em misleading}.
Clearly, we must now doubt  conclusions based on
``off-the-shelf'' tunings.
Further,
it is no longer enough to just run a data miner and report the result
{\em without} first conducting an tuning optimizations study.

@@

This section offers a small demonstration
of the impact of tuning parameters. It also demonstrates that this issue of tuning effects 
not just the complex data miners discussed later in the paper but also 
applies for even very simple  learning schemes.

@@

That researcher might test that belief by using studying historical
defect logs with 
linear regression. Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
software module (in this case, a  function).
Note that the Halstead correlation $c_2$
is worse than those from lines of code $c_1$. This result  seems to suggest that
despite their potential support for refactoring, our researchers should not use Halstead.

@@

The premise of DE  is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace
the old tuning $x_i$ with $y_i$:
\bi
\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item (For booleans) $y_i= \neg x_i$ (see line 37).
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates (which are generated
from the {\em Population}.

For this experiments of this paper, we collect performance
values from a data mining, from which a {\em Goal} function extracts one 
performance value$^{27}$ (so we tun this code many times, each time with
a different {\em Goal}$^2$).  Technically, this makes this a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).

@@

The following experimental aims to compare the performance of three learners, tuned and untuned, on 17
sets of data.

@@

Our defect data comes from the PROMISE repository\footnote{http://openscience.us/repo}.
It pertains to 
open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene}, {\it 
synapse}, {\it velocity}, {\it xalan} and {\it xerces}.

@@

For this experiment, we uses data sets with at least three  
consecutive releases  (where release $i+1$ was built after release $i$).
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
This approach ensures   all treatments 
are assessed on the same tests.

@@

In {\em Better-faster-cheaper}, we seek  project changes that lead
to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.

@@

   \caption{Ratios of defective instances in each experimental data set. 
   E.g., the top left data set has 20 defective classes out of 125 total.
   This paper runs one experiment for each column
   shown in this figure. The {\em training} set is used by an untuned learner
   to build a model, which is then tested on the {\em testing} data.
   {\em Training} data is used by  differential evolution when it builds
    a model (using one set of possible tunings) and that model is tested on {\em tunings}.
    Finally, the best model from by DE is applied to {\em testing}.  
   }\label{fig:data1}
\end{figure*}

@@

All the above vary from zero to one. For $pf$, the {\em better} scores and {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.

@@

These results offer support for the prior conclusions of  
 Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
\bi
\item
Untuned CART is indeed the worst learner (none of its
untuned results are best and {\bf bold}). 
\item 
In $\frac{15}{17}$ cases, untuned Random Forest out-performs  untuned CART.  
\ei
Some of the data sets in \fig{precisionbars} proved challenging for all learners;
e.g. the precision results for {\em ivy} are less
that impressive.
To some extend, this can be explained by
the properties of of the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare).

@@

\subsection{Tuning Changes Learner Rankings}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better is another~\cite{lessmann2008benchmarking,hall11,me07b}.
Such conclusions are   not reliable since they can change when we elect to tune for different goals.

@@

\scriptsize  
~~~\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
antV0 & {\bf 39} & {\rfour} & 25 & {\rtwo} & 32 & {\rthree} & 31 & {\rthree} & {\bf 39} & {\rfour} & 12 &        \\
antV1 & 11 &         & 6 &         & 40 & {\rfour} & {\bf 45} & {\rfour} & 39 & {\rfour} & 44 & {\rfour}\\
antV2 & 0 &         & {\bf 87} & {\rfour} & 44 & {\rtwo} & 1 &         & 50 & {\rtwo} & 51 & {\rtwo}\\
camelV0 & 0 &         & 28 & {\rfour} & 9 & {\rone} & 28 & {\rfour} & {\bf 34} & {\rfour} & 30 & {\rfour}\\
camelV1 & {\bf 34} & {\rfour} & {\bf 34} & {\rfour} & 31 &         & 32 & {\rone} & 33 & {\rthree} & 31 &        \\
ivyV0 & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
jeditV0 & 50 &         & 56 & {\rtwo} & 56 & {\rtwo} & 54 & {\rone} & {\bf 61} & {\rfour} & 59 & {\rfour}\\
jeditV1 & 37 & {\rone} & 33 &         & 36 &         & {\bf 49} & {\rfour} & 45 & {\rthree} & 47 & {\rfour}\\
jeditV2 & 4 &         & 8 & {\rtwo} & 5 &         & {\bf 11} & {\rfour} & 9 & {\rthree} & 9 & {\rthree}\\
log4jV0 & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
luceneV0 & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
poiV0 & {\bf 78} & {\rfour} & 64 &         & 74 & {\rthree} & 68 & {\rone} & 73 & {\rthree} & 69 & {\rone}\\
poiV1 & 5 &         & {\bf 78} & {\rfour} & 21 & {\rone} & {\bf 78} & {\rfour} & 76 & {\rfour} & {\bf 78} & {\rfour}\\
synapseV0 & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
velocityV0 & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
xercesV0 & 22 & {\rone} & 20 &         & 21 &         & {\bf 27} & {\rfour} & 23 & {\rtwo} & 20 &        \\
xercesV1 & 25 &         & 39 & {\rone} & 18 &         & 53 & {\rthree} & 68 & {\rfour} & {\bf 73} & {\rfour}\\
\end{tabular}
\caption{F-value results (best results  shown in {\bf bold}).}
\label{fig:fbars}
\end{figure}

@@

\fig{counts} shows how the objective goal (in this case,
{\em pd} (recall) or precision, or the f-measure) changed what attributes were used
in the decision tree learners
(in this case, WHERE building trees to select for different clusters).

@@

To see this,
recall from Algorithm~1 that
DE explores a {\em Population} of size {\em np=10}. This is a very small population size since
Rainer Storm (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
of attributes being optimized~\cite{storn1997differential}.

@@

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r|c |c |c |c |c |c }
    \hline\hline
    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
    \hline
    antV0 & 50 /  77.16 & 1.30 & 60 /  3.47 & 0.07 & 50 /  6.54 & 0.14\\
    antV1 & 50 /  135.16 & 2.33 & 60 /  4.84 & 0.08 & 50 /  8.61 & 0.19\\
    antV2 & 50 /  368.50 & 6.23 & 60 /  6.67 & 0.14 & 50 /  11.75 & 0.40\\
    camelV0 & 50 /  479.03 & 8.25 & 60 /  11.73 & 0.18 & 60 /  15.69 & 0.31\\
    camelV1 & 60 /  1551.51 & 26.87 & 60 /  18.47 & 0.28 & 80 /  37.96 & 0.73\\
    ivyV0 & 80 /  83.80 & 1.01 & 50 /  3.07 & 0.07 & 60 /  7.63 & 0.17\\
    jeditV0 & 60 /  349.99 & 5.95 & 70 /  8.33 & 0.11 & 50 /  13.40 & 0.30\\
    jeditV1 & 50 /  442.35 & 7.48 & 70 /  8.63 & 0.11 & 70 /  15.52 & 0.37\\
    jeditV2 & 50 /  360.04 & 7.90 & 60 /  8.63 & 0.12 & 60 /  14.33 & 0.38\\
    log4jV0 & 60 /  97.23 & 1.49 & 70 /  3.31 & 0.06 & 80 /  8.79 & 0.17\\
    luceneV0 & 70 /  206.41 & 2.89 & 80 /  6.90 & 0.08 & 60 /  10.30 & 0.25\\
    poiV0 & 70 /  338.44 & 4.28 & 60 /  6.47 & 0.13 & 60 /  12.45 & 0.29\\
    poiV1 & 60 /  468.73 & 7.95 & 50 /  7.24 & 0.14 & 70 /  17.66 & 0.30\\
    synapseV0 & 50 /  111.30 & 1.87 & 60 /  3.85 & 0.05 & 60 /  7.82 & 0.15\\
    velocityV0 & 60 /  192.83 & 2.66 & 90 /  6.11 & 0.06 & 80 /  12.99 & 0.22\\
    xercesV0 & 70 /  139.33 & 2.23 & 60 /  6.47 & 0.11 & 50 /  8.89 & 0.25\\
    xercesV1 & 50 /  759.82 & 13.11 & 50 /  8.62 & 0.14 & 60 /  16.90 & 0.37\\
  \end{tabular}
  \caption{Evaluations/runtimes  (in seconds), optimizing for  precision.  }\label{fig:etimes}
\end{figure*}

@@

\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline

>>>>

These results prompt for a change to standard methods in software analytics.
At least for defect prediction, 
it is no longer enough to just run a data miner and present the result
{\em without} first conducting a tuning optimization study.
The implications for other kinds of software analytics are now open and pressing questions.

@@

@@

To the best of our knowledge, this paper is the first extensive exploration 
of applying automatic optimizers to tune data miners for defect prediction,
(though see~\cite{cora10,balogh12,Minku13,minku13z} for tuning effort estimators).
The one similar study  we can find in the period 2004 to 2014\footnote{See the GECCO and SSBSE proceedings at    goo.gl/2MY602 and goo.gl/uzvU8e.} was
Bouktiff et al.~\cite{Bouktif06} who used  simulated annealing to tune Bayes classifiers.
That was a very limited study, applied to a  single defect data set.
The analysis of this paper is far more extensive and offers the following novel results:
\bi
\item
Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}
of those learners. 
\ei
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

Thirdly, it is a standard practice to use the default ``off-the-shelf'' tunings  for data mining tools (previously
we have defended that approach on methodological grounds arguing that it
encourages reproducibility~\cite{me15:book1}). That ``off-the-shelf''  policy
can no longer be condoned. For example, one such default setting
  in the Python \mbox{SciKitLearn} toolkit~\cite{scikit-learn}
is to use $F=10$ decision trees in  Random Forest classifiers.
Our optimizer settled on  $F$ values that were nowhere near that default:

@@

In summary, it is now an open and pressing research issue to check if
analytics without parameter tuning is considered {\em harmful} or, at the 
very least, {\em misleading}.
Clearly, we must now doubt  conclusions based on
``off-the-shelf'' tunings.
Further,
it is no longer enough to just run a data miner and report the result
{\em without} first conducting an tuning optimizations study.

@@

This section offers a small demonstration
of the impact of tuning parameters. It also demonstrates that this issue of tuning effects 
not just the complex data miners discussed later in the paper but also 
applies for even very simple  learning scheme.

@@

That researcher might test that belief by studying historical
defect logs with 
linear regression. Here are two equations (learned from the NASA data at goo.gl/pGDfvp)
that use just lines of code or the Halstead measures $N,V,L,D,I,E,B,T$ seen in a
software module (in this case, a  function).
Note that the Halstead correlation $c_2$
is worse than those from lines of code $c_1$. This result  seems to suggest that
despite their potential support for refactoring, our researchers should not use Halstead.

@@

The premise of DE  is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace
the old tuning $x_i$ with $y_i$:
\bi
\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item (For booleans) $y_i= \neg x_i$ (see line 37).
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates, which are generated
from the {\em Population}.

For the experiments of this paper, we collect performance
values from a data mining, from which a {\em Goal} function extracts one 
performance value$^{27}$ (so we run this code many times, each time with
a different {\em Goal}$^2$).  Technically, this makes a  {\em single objective} DE (and for notes on multi-objective DEs, see~\cite{Coello05,zhang07,5583335}).

@@

The following experiment aims to compare the performance of three learners, tuned and untuned, on 17
sets of data.

@@

Our defect data comes from the PROMISE repository\footnote{http://openscience.us/repo}.
It pertains to 
open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
{\it poi},{\it synapse}, {\it velocity} and {\it xerces}.

@@

For this experiment, we use data sets with at least three  
consecutive releases  (where release $i+1$ was built after release $i$).
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
This approach ensures   all treatments 
are assessed on the same tests.

@@

In {\em Better-faster-cheaper},   project want changes that lead
to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.

@@

   \caption{Ratios of defective instances in each experimental data set. 
   E.g., the top left data set has 20 defective classes out of 125 total.
   This paper runs one experiment for each column
   shown in this figure. The {\em training} set is used by an untuned learner
   to build a model, which is then tested on the {\em testing} data.
   {\em Training} data is used by  differential evolution when it builds
    a model (using one set of possible tunings) and that model is tested on {\em tuning} data.
    Finally, the best model from by DE is applied to {\em testing}.  
   }\label{fig:data1}
\end{figure*}

@@

All the above vary from zero to one. For $pf$, the {\em better} scores are {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.

@@

These results offer support for the prior conclusions of  
 Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
\bi
\item
Untuned CART is indeed the worst learner (none of its
untuned results are best and {\bf bold}). 
\item 
In $\frac{15}{17}$ cases, untuned Random Forest out-performs  untuned CART.  
\ei
Some of the data sets in \fig{precisionbars} proved challenging for all learners;
e.g. the precision results for {\em ivy} are less
that impressive.
To some extent, this can be explained by
the properties of of the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).

@@

\subsection{Tuning Changes Learner Rankings}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,hall11,me07b}.
Such conclusions are   not reliable since they can change when we elect to tune for different goals.

@@

\scriptsize  
~~~\begin{tabular}{r|rl|rl|rl|rl|rl|rlrl}
      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forest}         \\\hline
  Data set   &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{default}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{default}  &   \multicolumn{2}{c}{Tuned}\\\hline
antV0 & {\bf 39} & {\rfour} & 25 & {\rtwo} & 32 & {\rthree} & 31 & {\rthree} & {\bf 39} & {\rfour} & 12 &        \\
antV1 & 11 &         & 6 &         & 40 & {\rfour} & {\bf 45} & {\rfour} & 39 & {\rfour} & 44 & {\rfour}\\
antV2 & 0 &         & {\bf 87} & {\rfour} & 44 & {\rtwo} & 1 &         & 50 & {\rtwo} & 51 & {\rtwo}\\
camelV0 & 0 &         & 28 & {\rfour} & 9 & {\rone} & 28 & {\rfour} & {\bf 34} & {\rfour} & 30 & {\rfour}\\
camelV1 & {\bf 34} & {\rfour} & {\bf 34} & {\rfour} & 31 &         & 32 & {\rone} & 33 & {\rthree} & 31 &        \\
ivy & 27 &         & 34 & {\rthree} & 30 & {\rone} & {\bf 38} & {\rfour} & 35 & {\rthree} & 33 & {\rtwo}\\
jeditV0 & 50 &         & 56 & {\rtwo} & 56 & {\rtwo} & 54 & {\rone} & {\bf 61} & {\rfour} & 59 & {\rfour}\\
jeditV1 & 37 & {\rone} & 33 &         & 36 &         & {\bf 49} & {\rfour} & 45 & {\rthree} & 47 & {\rfour}\\
jeditV2 & 4 &         & 8 & {\rtwo} & 5 &         & {\bf 11} & {\rfour} & 9 & {\rthree} & 9 & {\rthree}\\
log4j & {\bf 62} & {\rfour} & 56 & {\rthree} & 47 & {\rone} & 59 & {\rfour} & 53 & {\rtwo} & 43 &        \\
lucene & 70 & {\rthree} & {\bf 75} & {\rfour} & 56 &         & {\bf 75} & {\rfour} & 73 & {\rfour} & {\bf 75} & {\rfour}\\
poiV0 & {\bf 78} & {\rfour} & 64 &         & 74 & {\rthree} & 68 & {\rone} & 73 & {\rthree} & 69 & {\rone}\\
poiV1 & 5 &         & {\bf 78} & {\rfour} & 21 & {\rone} & {\bf 78} & {\rfour} & 76 & {\rfour} & {\bf 78} & {\rfour}\\
synapse & 0 &         & 2 &         & 40 & {\rthree} & {\bf 56} & {\rfour} & 51 & {\rfour} & 55 & {\rfour}\\
velocity & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & 49 &         & {\bf 51} & {\rfour} & {\bf 51} & {\rfour} & {\bf 51} & {\rfour}\\
xercesV0 & 22 & {\rone} & 20 &         & 21 &         & {\bf 27} & {\rfour} & 23 & {\rtwo} & 20 &        \\
xercesV1 & 25 &         & 39 & {\rone} & 18 &         & 53 & {\rthree} & 68 & {\rfour} & {\bf 73} & {\rfour}\\
\end{tabular}
\caption{F-value results (best results  shown in {\bf bold}).}
\label{fig:fbars}
\end{figure}

@@

\fig{counts} shows how the objective goal (in this case,
 precision or the f-measure) changed what attributes were used
in the decision tree learners
(in this case, WHERE building trees to select for different clusters).

@@

To see this,
recall from Algorithm~1 that
DE explores a {\em Population} of size {\em np=10}. This is a very small population size since
Rainer Storn (one of the inventors of DE) recommends  setting {\em np} to be ten times larger than the number
of attributes being optimized~\cite{storn1997differential}.

@@

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r|c |c |c |c |c |c }
    \hline\hline
    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
    \hline
    antV0 & 50 /  77.16 & 1.30 & 60 /  3.47 & 0.07 & 50 /  6.54 & 0.14\\
    antV1 & 50 /  135.16 & 2.33 & 60 /  4.84 & 0.08 & 50 /  8.61 & 0.19\\
    antV2 & 50 /  368.50 & 6.23 & 60 /  6.67 & 0.14 & 50 /  11.75 & 0.40\\
    camelV0 & 50 /  479.03 & 8.25 & 60 /  11.73 & 0.18 & 60 /  15.69 & 0.31\\
    camelV1 & 60 /  1551.51 & 26.87 & 60 /  18.47 & 0.28 & 80 /  37.96 & 0.73\\
    ivy & 80 /  83.80 & 1.01 & 50 /  3.07 & 0.07 & 60 /  7.63 & 0.17\\
    jeditV0 & 60 /  349.99 & 5.95 & 70 /  8.33 & 0.11 & 50 /  13.40 & 0.30\\
    jeditV1 & 50 /  442.35 & 7.48 & 70 /  8.63 & 0.11 & 70 /  15.52 & 0.37\\
    jeditV2 & 50 /  360.04 & 7.90 & 60 /  8.63 & 0.12 & 60 /  14.33 & 0.38\\
    log4j & 60 /  97.23 & 1.49 & 70 /  3.31 & 0.06 & 80 /  8.79 & 0.17\\
    lucene & 70 /  206.41 & 2.89 & 80 /  6.90 & 0.08 & 60 /  10.30 & 0.25\\
    poiV0 & 70 /  338.44 & 4.28 & 60 /  6.47 & 0.13 & 60 /  12.45 & 0.29\\
    poiV1 & 60 /  468.73 & 7.95 & 50 /  7.24 & 0.14 & 70 /  17.66 & 0.30\\
    synapse & 50 /  111.30 & 1.87 & 60 /  3.85 & 0.05 & 60 /  7.82 & 0.15\\
    velocity & 60 /  192.83 & 2.66 & 90 /  6.11 & 0.06 & 80 /  12.99 & 0.22\\
    xercesV0 & 70 /  139.33 & 2.23 & 60 /  6.47 & 0.11 & 50 /  8.89 & 0.25\\
    xercesV1 & 50 /  759.82 & 13.11 & 50 /  8.62 & 0.14 & 60 /  16.90 & 0.37\\
  \end{tabular}
  \caption{Evaluations/runtimes  (in seconds), optimizing for  precision.  }\label{fig:etimes}
\end{figure*}

%%%%time for F %%%%%%
\begin{figure*}[!ht]
\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r|c |c |c |c |c |c }
    \hline\hline
    Datasets & Tuned\_Where & Default\_Where & Tuned\_CART & Default\_CART & Tuned\_RanFst & Default\_RanFst\\
    \hline
    antV0 & 70 / 95.34 & 1.18 & 50 / 3.09 & 0.06 & 60 / 6.89 & 0.13\\
    antV1 & 50 / 130.69 & 2.24 & 50 / 4.47 & 0.08 & 60 / 9.03 & 0.19\\
    antV2 & 50 / 296.68 & 6.66 & 60 / 7.29 & 0.15 & 60 / 12.74 & 0.31\\
    camelV0 & 60 / 496.70 & 8.01 & 60 / 10.43 & 0.17 & 70 / 17.32 & 0.30\\
    camelV1 & 70 / 1732.99 & 23.35 & 60 / 15.93 & 0.22 & 60 / 24.71 & 0.71\\
    ivy & 70 / 58.81 & 1.03 & 70 / 4.07 & 0.06 & 60 / 7.37 & 0.16\\
    jeditV0 & 90 / 412.23 & 5.17 & 70 / 6.59 & 0.08 & 60 / 10.56 & 0.28\\
    jeditV1 & 70 / 425.18 & 6.61 & 60 / 6.15 & 0.10 & 60 / 13.00 & 0.31\\
    jeditV2 & 60 / 398.86 & 6.97 & 50 / 5.90 & 0.12 & 60 / 13.63 & 0.35\\
    log4j & 50 / 68.17 & 1.37 & 60 / 2.46 & 0.04 & 70 / 6.37 & 0.15\\
    lucene & 50 / 147.78 & 2.74 & 50 / 3.79 & 0.07 & 60 / 7.98 & 0.24\\
    poiV0 & 60 / 251.48 & 3.90 & 60 / 5.65 & 0.09 & 70 / 11.25 & 0.30\\
    poiV1 & 60 / 404.96 & 7.22 & 70 / 8.10 & 0.11 & 60 / 12.74 & 0.28\\
    synapse & 50 / 95.37 & 1.80 & 60 / 3.69 & 0.06 & 60 / 7.65 & 0.14\\
    velocity & 60 / 176.80 & 3.40 & 50 / 4.14 & 0.07 & 50 / 7.36 & 0.23\\
    xercesV0 & 60 / 177.48 & 2.34 & 50 / 6.53 & 0.09 & 50 / 14.91 & 0.33\\
    xercesV1 & 50 / 762.28 & 13.33 & 70/ 12.84 & 0.15 & 60/ 16.63 & 0.40\\
  \end{tabular}
  \caption{Evaluations/runtimes  (in seconds), optimizing for  ``F''.  }\label{fig:ftimes}
\end{figure*}

@@

\resizebox{\textwidth}{!}{
\renewcommand{\baselinestretch}{0.9}
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline

  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivy&jeditV0&jeditV1&jeditV2&log4j&lucene&poiV0&poiV1&synapse&velocity&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.02& 0.72& 0.97& 0.01& 0.87& 1& 0.59& 0.49& 0.77& 0.38& 0.25& 0.94& 0.01& 0.81& 0.53& 0.83& 0.99\\ \cline{2-20}
& infoPrune& 0.33& 0.13& 0.64& 0.57& 0.33& 0.92& 0.37& 0.43& 0.53& 0.68& 0.56& 0.55& 0.74& 0.04& 0.34& 0.62& 1& 0.36\\ \cline{2-20}
& min\_sample\_split& 4& 5& 1& 1& 5& 3& 3& 8& 9& 2& 4& 6& 2& 2& 2& 2& 9& 7\\ \cline{2-20}
& min\_Size& 0.5& 0.59& 0.56& 0.29& 0.03& 0.64& 0.5& 1.0& 0.45& 1& 0.79& 0.22& 0.97& 1& 0.6& 0.68& 0.47& 0.35\\ \cline{2-20}
& wriggle& 0.2& 0.51& 0.88& 0.92& 0.67& 0.81& 0.82& 0.45& 0.93& 0.39& 0.92& 0.16& 0.48& 0.22& 0.98& 0.7& 0.57& 0.02\\ \cline{2-20}
& depthMin& 2& 4& 2& 5& 3& 2& 1& 5& 2& 2& 1& 3& 3& 3& 1& 4& 2& 5\\ \cline{2-20}
& depthMax& 10& 16& 12& 1& 11& 19& 12& 20& 7& 8& 17& 19& 17& 12& 9& 9& 13& 3\\ \cline{2-20}
& wherePrune& False& True& True& False& False& False& True& False& False& True& False& False& True& False& False& False& False& False\\ \cline{2-20}
& treePrune& True& True& False& False& False& True& False& False& False& True& True& False& False& False& False& True& False& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.06& 0.63& 0.99& 0.01& 1& 0.98& 0.47& 0.74& 0.99& 0.36& 0.6& 0.95& 0.01& 0.01& 0.01& 0.43& 0.01\\ \cline{2-20}
& max\_feature& None& 0.3& 0.81& 0.01& 1& 0.98& 0.26& 0.36& 0.76& 0.29& 0.5& 0.12& 0.01& 0.01& 0.01& 0.16& 0.96& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 13& 10& 15& 14& 13& 7& 7& 4& 5& 5& 15& 20& 8& 20& 6& 10& 2\\ \cline{2-20}
& min\_samples\_leaf& 1& 9& 17& 1& 9& 1& 20& 1& 20& 17& 4& 9& 3& 12& 10& 16& 4& 8\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.92& 0.49& 0.24& 0.01& 1& 1& 1& 1& 1& 0.7& 0.21& 1& 0.01& 0.17& 0.4& 0.81& 0.01\\ \cline{2-20}
& max\_feature& None& 0.02& 0.55& 0.01& 0.01& 0.81& 0.52& 0.01& 0.76& 0.01& 0.01& 0.67& 0.3& 0.01& 0.06& 0.36& 0.34& 0.93\\ \cline{2-20}
& max\_leaf\_nodes& None& 13& 10& 34& 10& 15& 25& 34& 24& 40& 20& 33& 14& 27& 40& 47& 44& 41\\ \cline{2-20}
& min\_samples\_split& 2& 8& 1& 15& 15& 10& 11& 10& 5& 1& 9& 6& 7& 13& 13& 12& 15& 15\\ \cline{2-20}
& min\_samples\_leaf& 1& 2& 14& 17& 19& 5& 13& 5& 2& 3& 11& 17& 2& 5& 9& 7& 18& 14\\ \cline{2-20}
& n\_estimators& 100& 132& 50& 81& 150& 63& 59& 85& 141& 96& 106& 71& 95& 121& 135& 112& 104& 92\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of ``F''.}\label{fig:fselect}
\end{figure*}
